Lab2

### 2021-07-29 src/data/DataCleaning.Rmd
generated covid_trips interim csv

# d_openings$State.Postal.Code <- d_openings$State.Abbreviation
# d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)
```
```{r export interim dataframe as csv, echo=FALSE}

```

>>>>

# d_openings$State.Postal.Code <- d_openings$State.Abbreviation
# d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)
```
```{r export interim dataframe as csv, echo=FALSE}
write.csv(d, '../../data/interim/covid_trips_interim.csv')
```
